### 2021-03-02 math/ia_2021/paper.tex
mu-update
ia work

\begin{document}
\doublespacing % Double spacing throughout the document

@@

% Suppresses headers, footers, and page numbers on title page
\begin{titlepage}
    \begin{center}
        \vspace*{4cm}
        A statistical approach to predicting a tsunami’s wave height \\
        \vspace{1cm}
        Can the height of a tsunami's wave be predicted based on the distance from and
        the magnitude of a preceding earthquake? \\
        \vspace{1cm}
        \textit{Väinö-verneri Kauppila} \\
        February 2021 \\
        \vspace{4cm}
        Word count: TBD \\
        \textit{Note: diagrams reserve a large amount of space, and cannot be placed in 
        the appendix for the sake of clarity}
        \vfill
        \vspace{0.1cm}
    \end{center}
\end{titlepage}

@@

So the regression line can be expressed as $\hat y = 5.60 x -618.01$

@@

@@

\begin{tikzpicture}[scale=1.1]
    \begin{axis}[
            title={Comparing X and Y},
            xlabel={X axis},
            ylabel={Y axis},
            xmin=300, xmax=1000,
            ymin=0, ymax=5500,
            ytick={0,1000,2000,3000,4000,5000},
            xtick={0,400,500,600,700,800,900},
            legend pos=north west,
            ymajorgrids=true,
            grid style=dashed,
            scale=1.2
        ]

@@

    \end{axis}
\end{tikzpicture}

>>>>

\begin{document}
%\doublespacing % Double spacing throughout the document

@@

% Suppresses headers, footers, and page numbers on title page
\begin{titlepage}
    \begin{center}
        \vspace*{4cm}
        A statistical approach to predicting a tsunami’s wave height \\
        \vspace{1cm}
        Can the height of a tsunami's wave be predicted based on the distance from and
        the magnitude of a preceding earthquake? \\
        \vspace{1cm}
        \textit{Väinö-verneri Kauppila} \\
        February 2021 \\
        \vspace{4cm}
        Word count: TBD
        \vfill
        \vspace{0.1cm}
    \end{center}
\end{titlepage}

@@

So the regression line can be expressed as $\boxed{\hat y = 5.60 x -618.01}$

@@

\section*{Notes}
\label{sec:notes}
\addcontentsline{toc}{section}{\nameref{sec:notes}}

All figures are generated through the use of TikZ (Tantau) and the Python library 
\verb|matplotlib|. This paper is written with the aid of the typesetting software \LaTeX. 
On a PDF viewer, the sections in the table of contents can be clicked to access that 
section.

@@

\begin{center}
    \begin{tikzpicture}[scale=1.1]
        \begin{axis}[
                title={Comparing X and Y},
                xlabel={X axis},
                ylabel={Y axis},
                xmin=300, xmax=1000,
                ymin=0, ymax=5500,
                ytick={0,1000,2000,3000,4000,5000},
                xtick={0,400,500,600,700,800,900},
                legend pos=north west,
                ymajorgrids=true,
                grid style=dashed,
                scale=1.2
            ]

@@

        \end{axis}
    \end{tikzpicture}
\end{center}
